Adaptive Waveform Inversion for Transmitted Wavefields

### 2024-10-18 repro/papers/awi/paper.tex
more

Hadamard's construction is local, in both space-time and in the set of
acoustic models. A {\em normal neighborhood} of
$\bx_s \in \bR^3$ is an open subset of $\bR^3$ 
within which every point is connected to $\bx_s$ by  a unique ray of
geometric acoustics (a geodesic for the Riemannian metric associated
to the equation \ref{eqn:awe2}) (\cite{Friedlander:75},
p. 16). Hadamard's decomposition holds in a space-time cylinder
$\Omega \times \bR$,  and $\Omega\subset \bR^3$ 
and $M \subset C^{\infty}(\bR^3) \cap L^{\infty}(\bR^3)$ are bounded open sets satisfying 
\begin{itemize}
  \item[G1. ] $X_{sr} \subset \Omega \times \Omega$;
  \item[G2. ] for every source point $\bx_s\in X_{s}$ and $\log \kappa \in M$, $\Omega$ is a
    normal neighborhood of $\bx_s$.
  \item[G3. ] for every source point $\bx_s \in X_{s};$
    $\log \kappa \in M$, ray ${\bf X}:\bR^+\rightarrow \bR^3$
    with ${\bf X}(0)=\bx_s$ and any $t>0$, either $\{{\bf X}(s): 0\le s \le t\} \subset \Omega$
    or $\{{\bf X}(s): t < s < \infty\} \subset \bR^3 \setminus \Omega$.
  \end{itemize}
Condition G3 (the ``no return'' condition) means that once a ray
leaves $\Omega$, it does not return to $\Omega$. Conditions G1 - G3
hold for any convex open set $\Omega$ if $\kappa$ is constant, and for small perturbations and some
large perturbations of constant $\kappa$: these are open conditions in
the topology of $M$.

@@

Under conditions G1 - G4, the construction described by
\cite{Friedlander:75} produces for each $m \in M$ functions $\tau[\kappa]$ (travel time), $a[\kappa]$
(geometric amplitude) on $X_s \times \Omega$ and $b[\kappa]$
(remainder kernel) on $X_s \times \Omega \times \bR$, satisfying
\begin{itemize}
\item[H1. ] $\tau[\kappa], a[\kappa],$ and $b[\kappa]$ are smooth off the diagonal,
that is, $\tau[\kappa](\bx_s,\cdot) \in C^{\infty}(\Omega \setminus \{\bx_s\})$
and similarly for $a[\kappa],b[\kappa]$;
\item[H2. ] there exists $A>0$ so that for any $\log \kappa \in M$
  and $(\bx_s,\bx_r) \in X_{sr}$,
  $|\log a[\kappa](\bx_s,\bx_r)| < A$;
\item[H3. ] there exist $B \ge 0,\delta > 0$ so that for
$(\bx_s,\bx_r) \in X_{sr}$, and $\kappa \in
M$,
\begin{eqnarray}
  |b[\kappa](\bx_r,t;\bx_r,s)| &\le& B e^{-\delta t} \nonumber \\
  |\partial_t b[\kappa](\bx_r,t;\bx_r,s)| &\le& B e^{-\delta t}
  \label{eqn:best}
\end{eqnarray}
\end{itemize}
(The exponential decay estimate in item H3 follows from hypothesis G4.)

@@

@@

For such extended sources,
\[
  \bar{F}[\kappa,u*w] = u*F[\kappa]
\]
Introduce the notation $S[\kappa]$ for the operator of convolution
with $F[\kappa]$, that is,
\begin{equation}
  \label{eqn:sdef}
  S[\kappa]u \equiv u*F[\kappa]
\end{equation}
Then $S[\kappa]$ is bounded on $L^2(X_{sr} \times \bR)$, uniformly in
$\log \kappa \in M$, thanks to
the bound \ref{eqn:fwdnorm} for $p=1$. $S$ also represents an
extension of $F$, in the sense that with the choice
$u(\bx_r,t;\bx_s)=\delta(t)$, the output of $F$ is recovered:
\begin{equation}
  \label{eqn:sconsist}
  S[\kappa]\delta = F[\kappa].
\end{equation}

@@

In fact, these two defects are really symptoms of the instability of
deconvolution for kernels with the properties of $F[\kappa]$.  To
begin with, $S[\kappa] = F[\kappa]*$ defines a bounded map on
$L^2(X_{sr}\times \bR)$, since from \ref{eqn:fwdgreen} and the definition of
  $S[\kappa]$,
\[
  S[\kappa]u = \rho( a[\kappa]\delta    +  (b[\kappa]H)) *\delta_{\tau[\kappa]}*\partial_t f. *u,
\]
The bounds \ref{eqn:best} yield $bH \in
  L^1(X_{sr}\times \bR)$, and property F1, $\partial_t f \in
  L^1(\bR)$.

The conventional remedy for instability in a deconvolution problem of
this type is so-called ``pre-whitening'', as
mentioned by \cite{Warner:16} ``Pre-whitening'' is a version of
Tihonov regularization. It  amounts to replacement of the equation
$S[\kappa]u=d$ by the regularized least squares problem: 
\begin{equation}
  \label{eqn:reg}
  u_{\sigma}[\kappa;d] = \mbox{argmin}_{u \in L^2(X_{sr} \times \bR)} (\|S[\kappa]u-d\|^2 + \sigma\|u\|^2)
\end{equation}
For $\sigma > 0$, the Lax-Milgram Theorem (\cite{Yosida}, section
III.7) implies that this least-squares problem has a unique solution
$u_{\sigma}[\kappa;d] \in L^2(X_{sr} \times \bR)$. Define the modified
AWI objective $J_{\rm AWI,\sigma}$ by
replacing $u$ in the definition \ref{eqn:awideforig} with $u_{\sigma}$:
\begin{equation}
  \label{eqn:awidef}
  J_{\rm AWI,\sigma}[\kappa;d] = \sum_{\bx_s,\bx_r} \left(\frac{\int dt |tu_{\sigma}[\kappa;d](\bx_r,t;\bx_s)|^2}{\int dt |u_{\sigma}[\kappa;d](\bx_r,t;\bx_s)|^2}\right). 
\end{equation}
To make this definition a bit more concise, introduce the operator $T$ on
${\cal D}'(X_{sr} \times \bR)$ by
\[
  Tp(\bx_r,t;\bx_s) = tp(\bx_r,t;\bx_s).
\]
Then
\begin{equation}
  \label{eqn:awidefbis}
  J_{\rm AWI,\sigma}[\kappa;d] = \sum_{(\bx_s,\bx_r) \in X_{sr}}
  \frac{\|Tu_{\sigma}[\kappa;d](\bx_r,\cdot;\bx_s)\|^2}{\|u_{\sigma}[\kappa;d](\bx_r,\cdot;\bx_s)\|^2}.
\end{equation}
Here $\| \cdot \|$ is the norm in $L^2(\bR)$.

@@

\begin{prop}
  \label{thm:tl2}
  Suppose that $d, Td \in L^2(X_{sr} \times \bR)$. Then
  $Tu_{\sigma}[\kappa;d]  \in L^2(X_{sr} \times \bR)$.
\end{prop}

@@

  Thus
  \[
    S^TS =
    \rho^2(a\delta  +  (\check{b}\check{H})) *\delta_{-\tau}*\partial_t
    f * (a\delta  +  (bH)) *\delta_{\tau}*\partial_t f*
  \]
  \[
    = \rho^2((a\delta  +  (\check{b}\check{H}))*(a\delta  +
    (bH))*\partial_t f *\partial_t f*
  \]
  \[
    [T,S^TS] = \rho^2((T\check{b}\check{H}) *(a\delta  +
    (bH))*+ (a\delta  +  (\check{b}\check{H}))*(TbH))*\partial_t f
    *\partial_t f*
  \]
  \begin{equation}
    \label{eqn:tsscomm}
    +2\rho^2((a\delta  +  (\check{b}\check{H}))*(a\delta  +
    (bH)))* \partial_t f  *T\partial_t f*.
  \end{equation}
  Referring to the exponential decay assumption \ref{eqn:best}
  and properties F1, F2 of $f$, 
  observe that all summands on the RHS of identity \ref{eqn:tsscomm} are in
  $L^1(X_{sr} \times \bR)$, so $[T,S^TS]$ restricts to a bounded
  operator on $L^2(X_{sr}\times \bR)$. A similar computation shows the
  same property for $[T,S^T]$. Since $u_{\sigma} \in L^2(X_{sr}\times
  \bR)$,
  \[
    T(S^TS+\sigma I)u_{\sigma} =  [T,(S^TS+\sigma I)]u_{\sigma} +
    (S^TS+\sigma I)Tu_{\sigma}
  \]
  \[
    = [T,S^T]d + S^TTd,
  \]
  that is,
  \[
    (S^TS+\sigma I)Tu_{\sigma} = e \in L^2(X_{sr} \times \bR).
  \]
  A theorem of von Neumann (\cite{Yosida}, VII.3, Theorem 2) implies
  that $S^TS+\sigma I$ has a bounded inverse, so the distribution
  $Tu_{\sigma} \in L^2(X_{sr} \times \bR)$.
\end{proof}

@@

\begin{prop}
  \label{thm:noisefree}
  Suppose that $\kappa \in M$ and $d = F[\kappa]$. Then $Td
  \in L^2(X_{sr} \times \bR)$.
\end{prop}

\begin{proof}
  A simple estimate shows that $F[\kappa]$ satisfies an exponential
  decay estimate of the form G4, whence the conclusion follows.
\end{proof}

@@

Similarly, define
\begin{eqnarray}
  \label{eqn:sdeflam}
  \Sl[\kappa]u &=& u *\Fl[\kappa],  \nonumber \\
  \Sla[\kappa]u &=& u *\Fla[\kappa], \nonumber\\
  \Slb[\kappa]u &=& u *\Flb[\kappa], 
\end{eqnarray}
so that
\[
  \Sl[\kappa] = \Sla[\kappa] + \Slb[\kappa].
\]
From the bound \ref{eqn:Frembd} for $p=1$, there is $C \ge 0$ so that
for all $\log \kappa \in M$, $u \in L^2(X_{sr} \times \bR)$,
\begin{eqnarray}
  \label{eqn:Srembd}
  \|\Sl[\kappa]u\| &\le&  C\lambda^{\frac{1}{2}}\|u\|,\nonumber \\
  \|\Slb[\kappa]u\| & \le& C\lambda^{\frac{3}{2}}\|u\|.
\end{eqnarray}

\subsection{Linking Regularization and Wavelength}
In the remainder of this section, I will examine the $\lambda$-parametrized families of
objective functions obtained by
\begin{itemize}
\item[1. ]replacing $S$ and $d$ in the definitions \ref{eqn:awidefbis}
  and \ref{eqn:mswidef} with $\Sl$ and $\dl =\Fl[\kappa^*]$, that is,
  noise-free data generated by a choice of $\kappa^* \in M$ and
  $\lambda \in (0,1]$, and
\item[2. ] choosing the Tihonov regularization weight
  $\sigma = \lambda$.
\end{itemize}
That is,
\begin{equation}
  \label{eqn:mswideflam}
  J_{\rm MSWI,\lambda}[\kappa;\dl] =  \|T\ul[\kappa;d]\|^2
\end{equation}
and 
\begin{equation}
  \label{eqn:awideflam}
  J_{\rm AWI,\lambda}[\kappa;\dl] = \sum_{(\bx_s,\bx_r) \in X_{sr}} 
  \frac{\|T\ul[\kappa;d](\bx_r,\cdot;\bx_s)\|^2}{\|\ul[\kappa;d](\bx_r,\cdot;\bx_s)\|^2}.
\end{equation}
In both definitions, $\ul$ solves the least-squares problem \ref{eqn:reg} with
$\sigma = \lambda$.

@@

%And that's ``why it works'' - when geometric asymptotics in the form
%given by equation \ref{eqn:hadamard} is an accurate approximation to
%the Green's function.

@@

>>>>

Hadamard's construction is local, in both space-time and in the set of
acoustic models. A {\em normal neighborhood} of
$\bx_s \in \bR^3$ is an open subset of $\bR^3$ 
within which every point is connected to $\bx_s$ by  a unique ray of
geometric acoustics (a geodesic for the Riemannian metric associated
to the equation \ref{eqn:awe2}) (\cite{Friedlander:75},
p. 16).

Throughtout the following discussion, $\Omega\subset \bR^3$ 
and $M \subset C^{\infty}(\bR^3) \cap L^{\infty}(\bR^3)$ are bounded open sets satisfying 
\begin{itemize}
  \item[G1. ] $X_{sr} \subset \Omega \times \Omega$;
  \item[G2. ] for every source point $\bx_s\in X_{s}$ and $\log \kappa \in M$, $\Omega$ is a
    normal neighborhood of $\bx_s$.
  \item[G3. ] for every source point $\bx_s \in X_{s};$
    $\log \kappa \in M$, ray ${\bf X}:\bR^+\rightarrow \bR^3$
    with ${\bf X}(0)=\bx_s$ and any $t>0$, either $\{{\bf X}(s): 0\le s \le t\} \subset \Omega$
    or $\{{\bf X}(s): t < s < \infty\} \subset \bR^3 \setminus \Omega$.
  \end{itemize}
Condition G3 (the ``no return'' condition) means that once a ray
leaves $\Omega$, it does not return to $\Omega$. Conditions G1 - G3
hold for any convex open set $\Omega$ if $\kappa$ is constant, and for small perturbations and some
large perturbations of constant $\kappa$: these are open conditions in
the topology of $M$.

@@

Under conditions G1 - G4, the construction described by
\cite{Friedlander:75} produces for each $m \in M$ functions $\tau[\kappa]$ (travel time), $a[\kappa]$
(geometric amplitude) on $X_s \times \Omega$ and $b[\kappa]$
(remainder kernel) on $X_s \times \Omega \times \bR$, satisfying
\begin{itemize}
\item[H1. ] $\tau[\kappa], a[\kappa],$ and $b[\kappa]$ are smooth off the diagonal,
that is, $\tau[\kappa](\bx_s,\cdot) \in C^{\infty}(\Omega \setminus \{\bx_s\})$
and similarly for $a[\kappa],b[\kappa]$;
\item[H2. ] there exists $A>0$ so that for any $\log \kappa \in M$
  and $(\bx_s,\bx_r) \in X_{sr}$,
  $|\log a[\kappa](\bx_s,\bx_r)| < A$;
\item[H3. ] for any $k \ge 0$, there exists $B \ge 0,\delta > 0$ so
  that for any $(\bx_s,\bx_r) \in X_{sr}$, $\kappa \in M$, 
\begin{equation}
  |\partial^k_t b[\kappa](\bx_r,t;\bx_r,s)| \le B e^{-\delta t}
  \label{eqn:best}
\end{equation}
\end{itemize}
(The exponential decay estimate in item H3 follows from hypothesis G4.)

@@

\subsection{Notational Conventions for Norms and Bounds}
The Banach spaces
$l^p(X_{sr},L^p(\bR))$ will be abbreviated as $L^p(X_{sr} \times
\bR)$. The norm in a Banach space $B$ will be denoted
$\|\cdot\|_{B}$. The norm symbol
$\|\cdot\|$ without subscript will be understood to mean either
$\|\cdot\|_{L^2(\bR)}$ or $\|\cdot\|_{L^2(X_{sr}\times
  \bR)}$, as context indicates.

In a statement pertaining to all
$\kappa \in M$, the letter $C$, or sometimes $C_k,
k=0,1,2,...$ or
$C_*,C^*$, will designate a constant (or constants) independent of
$\kappa$.

@@

For such extended sources,
\[
  \bar{F}[\kappa,u*w] = u*F[\kappa]
\]
Introduce the notation $S[\kappa]$ for the operator of convolution
with $F[\kappa]$, that is,
\begin{equation}
  \label{eqn:sdef}
  S[\kappa]u = u*F[\kappa]
\end{equation}
Then $S[\kappa]$ is bounded on $L^2(X_{sr} \times \bR)$, uniformly in
$\log \kappa \in M$, thanks to
the bound \ref{eqn:fwdnorm} for $p=1$. $S$ also represents an
extension of $F$, in the sense that with the choice
$u(\bx_r,t;\bx_s)=\delta(t)$, the output of $F$ is recovered:
\begin{equation}
  \label{eqn:sconsist}
  S[\kappa]\delta = F[\kappa].
\end{equation}

@@

In fact, these two defects are really symptoms of the instability of
deconvolution for kernels with the properties of $F[\kappa]$.  To
begin with, $S[\kappa] = F[\kappa]*$ defines a bounded map on
$L^2(X_{sr}\times \bR)$, since from \ref{eqn:fwdgreen} and the
definition \ref{eqn:sdef} of  $S[\kappa]$,
\[
  S[\kappa]u = \rho( a[\kappa]\delta    +  (b[\kappa]H)) *\delta_{\tau[\kappa]}*\partial_t f *u,
\]
\begin{equation}
  \label{eqn:sgood}
  = \rho(a[\kappa]\delta_{\tau[\kappa]}*\partial_t f +
  (b[\kappa](0)\delta + (\partial_t b[\kappa])H)
  *\delta_{\tau[\kappa]}*f) * u
\end{equation}
The key properties of $S$ follow directly from Young's inequality and
the representation \ref{eqn:fwdgreen}:
\begin{lemma}
  \label{thm:snorm}
  Under the assumptions leading to \ref{eqn:fwdgreen} and
  the properties F1 and F2, $S[\kappa]$ is a bounded operator on
  $L^2(X_{sr} \times \bR)$, and there exists $C>0$ so
  that for any $\kappa \in M$,
  \begin{equation}
    \label{eqn:snorm}
    \|S[\kappa]\| \le C\|\partial_t f\|_{L^1(\bR)}.
  \end{equation}
\end{lemma}

The conventional remedy for instability in a deconvolution problem of
this type is so-called ``pre-whitening'', as
mentioned by \cite{Warner:16} ``Pre-whitening'' is a version of
Tihonov regularization. It  amounts to replacement of the equation
$S[\kappa]u=d$ by the regularized least squares problem: 
\begin{equation}
  \label{eqn:reg}
  u_{\sigma}[\kappa;d] = \mbox{argmin}_{u \in L^2(X_{sr} \times \bR)} (\|S[\kappa]u-d\|^2 + \sigma\|u\|^2)
\end{equation}

\begin{prop}
  \label{thm:unorm}
  Under the assumptions G1 - G4 and F1, F2 justifying the
  representation \ref{eqn:fwdgreen}, the least squares problem
  \ref{eqn:reg} with $\sigma > 0$ has a unique solution
  $u_{\sigma}[\kappa;d] \in L^2(X_{sr} \times \bR)$ satisfying
  \begin{equation}
    \label{eqn:unorm}
    \|u_{\sigma}[\kappa;d]\| \le \frac{C}{\sigma}\|\partial_t f\|_{L^1(\bR)}\|d\|.
  \end{equation}
\end{prop}
\begin{proof}
For $\sigma > 0$, the Lax-Milgram Theorem (\cite{Yosida}, section
III.7) assures the existence of unique solution. 
\end{proof}

Define the modified
AWI objective $J_{\rm AWI,\sigma}$ by
replacing $u$ in the definition \ref{eqn:awideforig} with $u_{\sigma}$:
\begin{equation}
  \label{eqn:awidef}
  J_{\rm AWI,\sigma}[\kappa;d] = \sum_{\bx_s,\bx_r} \left(\frac{\int dt |tu_{\sigma}[\kappa;d](\bx_r,t;\bx_s)|^2}{\int dt |u_{\sigma}[\kappa;d](\bx_r,t;\bx_s)|^2}\right). 
\end{equation}
To make this definition a bit more concise, introduce the operator $T$ on
${\cal D}'(X_{sr} \times \bR)$ by
\[
  Tp(\bx_r,t;\bx_s) = tp(\bx_r,t;\bx_s).
\]
Then
\begin{equation}
  \label{eqn:awidefbis}
  J_{\rm AWI,\sigma}[\kappa;d] = \sum_{(\bx_s,\bx_r) \in X_{sr}}
  \frac{\|Tu_{\sigma}[\kappa;d](\bx_r,\cdot;\bx_s)\|^2}{\|u_{\sigma}[\kappa;d](\bx_r,\cdot;\bx_s)\|^2}.
\end{equation}
Here $\| \cdot \|$ is the norm in $L^2(\bR)$.

@@

\begin{prop}
  \label{thm:tl2}
  Suppose that $d, Td \in L^2(X_{sr} \times \bR)$. Then
  $Tu_{\sigma}[\kappa;d]  \in L^2(X_{sr} \times \bR)$, and
  \[
    \|Tu_{\sigma}[\kappa;d]\| \le
  \]
  \begin{equation}
    \label{eqn:tunorm}
    \frac{C}{\sigma}\left(\left(
        \frac{\|\partial_t f\|^2_{L^1(\bR)}}{\sigma}(\|f\|_{L^1(\bR)}+\|T\partial_tf\|_{L^1(\bR)})
      \right)\|d\| \\ 
    + \|\partial_t  f\|_{L^1(\bR)}(\|d\| +\|Td\|)\right).
  \end{equation}
\end{prop}

@@

  Thus
  \[
    S^TS =
    \rho^2(a\delta  +  (\check{b}\check{H})) *\delta_{-\tau}*\partial_t
    f * (a\delta  +  (bH)) *\delta_{\tau}*\partial_t f*
  \]
  \[
    = \rho^2((a\delta  +  (\check{b}\check{H}))*(a\delta  +
    (bH))*\partial_t f *\partial_t f*
  \]
  \[
    [T,S^TS] = \rho^2((T\check{b}\check{H}) *(a\delta  +
    (bH))*+ (a\delta  +  (\check{b}\check{H}))*(TbH))*\partial_t f
    *\partial_t f*
  \]
  \[
    +2\rho^2((a\delta  +  (\check{b}\check{H}))*(a\delta  +
    (bH)))* \partial_t f  *T\partial_t f*
  \]
  \[
    =\rho^2((T\partial_t\check{b}\check{H}) *(a\delta  +
    (bH))*+ (a\delta  +  (\check{b}\check{H}))*(T\partial bH))* f
    *\partial_t f*
   \]
  \begin{equation}
    \label{eqn:tsscomm}
     +2\rho^2((a\delta  +  (\check{b}\check{H}))*(a\delta  +
    (bH)))* \partial_t f  *T\partial_t f*.
  \end{equation}

  Referring to the exponential decay assumption \ref{eqn:best}
  and properties F1, F2 of $f$, 
  observe that all summands on the RHS of identity \ref{eqn:tsscomm} are in
  $L^1(X_{sr} \times \bR)$, so $[T,S^TS]$ restricts to a bounded
  operator on $L^2(X_{sr}\times \bR)$, with
  \begin{equation}
    \label{eqn:tsscommnorm}
    \|[T,S^TS]\| \le C\|\partial_t f\|_{L^1(\bR)}(\|f\|_{L^1(\bR)}+\|T\partial_tf\|_{L^1(\bR)})
  \end{equation}

  Similarly,
  \[
    [T,S]=T(\partial_t b)H*\delta_{\tau}*f + \tau(a\delta +
    bH)*\delta_{\tau}*\partial_t f + (a\delta +
    bH)*\delta_{\tau}*T\partial_t f.
  \]
  Young's inequality shows that the RHS lies in $L^1(X_{sr}\times
  \bR)$, and that there exists $C$ independent of $\kappa$ so that
  $[T,S^T]$ obeys the same estimate as does $S$ (Lemma
  \ref{thm:snorm}), that is,
  \begin{equation}
    \label{eqn:tcommst}  
    \|[T,S^T]\| = \|[T,S]\| \le C\|\partial_t f\|_{L^1(\bR)}
  \end{equation}

  Multiplying the normal equation for $u_{\sigma}$Rearranging,
  \[
    (S^TS+\sigma I)Tu_{\sigma} = -[T,S^TS]u_{\sigma} + [T,S^T]d + S^TTd.
  \]
  A theorem of von Neumann (\cite{Yosida}, VII.3, Theorem 2) implies
  that $S^TS+\sigma I$ has a bounded inverse, so the distribution
  $Tu_{\sigma} \in L^2(X_{sr} \times \bR)$. The inverse is bounded by
  $1/\sigma$, so the estimates \ref{eqn:snorm}, \ref{eqn:unorm},
  \ref{eqn:tcommst}, and \ref{eqn:tsscommnorm} combine to yield the
  bound \ref{eqn:tunorm}.

@@

\begin{prop}
  \label{thm:noisefree}
  Suppose that $\kappa \in M$. Then for $p \ge 1$, $F[\kappa], TF[\kappa]
  \in L^p(X_{sr} \times \bR)$, and there exist $C_0, C_1, C_2 >0$ so that
  \begin{eqnarray}
    \label{eqn:dnorms}
    C_1\|\partial_tf\|_{L^p(\bR)} - C_2\|f\|_{L^p(\bR)} \le \|F[\kappa]\|_{L^p(\bR)} & \le & C_0\|\partial_tf\|_{L^p(\bR)}, \nonumber \\
    \|TF[\kappa]\|_{L^p(\bR)} & \le & C_0\|\partial_tf\|_{L^p(\bR)}.
  \end{eqnarray}
\end{prop}

\begin{proof}
  A simple estimate shows that $F[\kappa]$ satisfies an exponential
  decay estimate of the form G4, whence the first estimate
  follows. Since $TbH \in W^{1,1}(\bR)$,
  \[
    T\rho(a\delta + bH)*\delta_{\tau}*\partial_t f = \partial_t TbH *
    \delta_{\tau} * f + \tau \rho (a\delta +
    bH)*\delta_{\tau}*\partial_t f  + (a\delta +
    bH)*\delta_{\tau}*T\partial_t f.
  \]
  All terms involve convolution of $f$ or $\partial_t f$ with kernels
  uniformly $L^1$-bounded in $\kappa \in M$, so the second estimate follows. 
\end{proof}

@@

Similarly, define
\begin{eqnarray}
  \label{eqn:sdeflam}
  \Sl[\kappa]u &=& u *\Fl[\kappa],  \nonumber \\
  \Sla[\kappa]u &=& u *\Fla[\kappa], \nonumber\\
  \Slb[\kappa]u &=& u *\Flb[\kappa], 
\end{eqnarray}
so that
\[
  \Sl[\kappa] = \Sla[\kappa] + \Slb[\kappa].
\]
From the bound \ref{eqn:Frembd} for $p=1$, there is $C \ge 0$ so that
for all $\log \kappa \in M$, $u \in L^2(X_{sr} \times \bR)$,
\begin{eqnarray}
  \label{eqn:Srembd}
  \|\Sl[\kappa]\| &\le&  C\lambda^{\frac{1}{2}},\nonumber \\
  \|\Sla[\kappa]\|& \le& C\lambda^{\frac{1}{2}}. \nonumber \\
  \|\Slb[\kappa]\| & \le& C\lambda^{\frac{3}{2}}.
\end{eqnarray}

\subsection{Linking Regularization and Wavelength}
In the remainder of this section, I will examine the $\lambda$-parametrized families of
objective functions obtained by
\begin{itemize}
\item[1. ]replacing $S$ and $d$ in the definitions \ref{eqn:awidefbis}
  and \ref{eqn:mswidef} with $\Sl$ and $\dl =\Fl[\kappa^*]$, that is,
  noise-free data generated by a choice of $\kappa^* \in M$ and
  $\lambda \in (0,1]$, and
\item[2. ] choosing the Tihonov regularization weight
  $\sigma = \lambda$.
\end{itemize}
That is,
\begin{equation}
  \label{eqn:mswideflam}
  J_{\rm MSWI,\lambda}[\kappa;\dl] =  \|T\ul[\kappa;\dl]\|^2
\end{equation}
and 
\begin{equation}
  \label{eqn:awideflam}
  J_{\rm AWI,\lambda}[\kappa;\dl] = \sum_{(\bx_s,\bx_r) \in X_{sr}} 
  \frac{\|T\ul[\kappa;\dl](\bx_r,\cdot;\bx_s)\|^2}{\|\ul[\kappa;\dl](\bx_r,\cdot;\bx_s)\|^2}.
\end{equation}
In both definitions, $\ul$ solves the least-squares problem \ref{eqn:reg} with
$\sigma = \lambda$.

@@

\begin{prop} Under the hypotheses of Proposition \ref{thm:leading},
  \begin{eqnarray}
    \label{eqn:diffests}
    \|\ul-\uzl\| &\le& C \nonumber \\
    \|T(\ul-\uzl)\| &\le& C
  \end{eqnarray}
\end{prop}

\begin{proof}
  A little algebra yields
  \begin{equation}
    \label{eqn:step1}
    ((\Sla)^T\Sla + \lambda I) (u_{\lambda}-\uzl) = (\Slb)^T d_{\lambda} + (\Sla)^T(d_{\lambda}-d_{0,\lambda})- 
    ((\Sla)^T\Slb + (\Slb)^T\Sla + (\Slb)^T\Slb)u_{\lambda}
  \end{equation}
  Note that the bounds \ref{eqn:Srembd} imply
\[
  \|(\Sla)^T (\dl-\dzl)\| = \|(\Sla)^T(\rho \fl b^*(0)\delta +
  \rho \fl*(\partial_tb^*H)*\delta_{\tau^*}\|
\]
\[
  = \rho \|a \wl * \fl * (b^*(0)\delta - \partial_tb^*H)\|
  \le C \lambda^{\frac{3}{2}}\|\dl\|
\]
and similarly
\[
 \| (\Slb)^T\dl \| \le C \lambda^{3/2}\|\dl\|.
\]
A bit more algebra gives
\[
  (\Sla)^T\Slb + (\Slb)^T\Sla + (\Slb)^T\Slb = \rho^2 (c \delta + g) *
  \fl * \fl *,
\]
in which
\[
  c = 2a \partial t b(0) - b(0)^2)
\]
and
\[
  g = a(\partial^2_t b H + \partial^2_t \check{b}\check{H}) -
  b((0)((\partial_t \check{b}) \check{H} + (\partial_t b) H +
  ((\partial_t \check{b}) \check{H})*((\partial_t b)H)) 
\]
According to Young's inequality and the bounds \ref{eqn:best}, $g$ is integrable with a 
$L^1(X_{sr}\times \bR)$ bound independent of $\log \kappa \in
M$. Therefore from the bounds \ref{eqn:lambdanorms}, obtain
\begin{equation}
  \label{eqn:step2}
\|(\Sla)^T\Slb + (\Slb)^T\Sla + (\Slb)^T\Slb\} \le C \lambda^3
\end{equation}
From the bounds \ref{eqn:unorm} and \ref{eqn:lambdanorms},
\[
  \|\ul\| \le C \lambda^{-\frac{1}{2}}\|\dl\|
\]
Combining the preceding results in the first estimate
\ref{eqn:diffests}.

%%%%%%%%%%%%%%%%%%%%%

over in the expression for $g$ is exponentially decaying, hence
%And that's ``why it works'' - when geometric asymptotics in the form
%given by equation \ref{eqn:hadamard} is an accurate approximation to
%the Green's function.

@@

On the other hand,
\[
  T(\dl - \dzl) = T(b^*H*\delta_{\tau^*}*\wl = T(b^*(0)\delta +
  \partial_t b^*H)*\delta_{\tau^*} *\fl
\]
\[
  (T\partial_tb^*H)*\delta_{\tau^*}*\fl+(b^*(0)\delta +
  \partial_t b^*H)\tau^*\delta_{\tau^*}*\fl +( b^*(0)\delta +
  \partial_t b^*H)*\delta_{\tau^*}T\fl
\]
From the second relation \ref{eqn:lambdanorms},
\begin{equation}
  \label{eqn:step7.5}
  \|T(\dl-\dzl)\| \le C \lambda
\end{equation}
in which $C$ depends on $M$ and on the support of $f_1$ (which
contains the support of $\fl$). The second bound \ref{eqn:rembd}
gives
\begin{equation}
  \label{step8}
  \Slb T(\dl-\dzl) \le C\lambda^{\frac{3}{2}}
\end{equation}
Also,
\[
  [T,\Slb] = ((Tb)H) *\wl * \delta_{\tau}* + (bH) * T\wl *
delta_{\tau} * + \tau (bH)* \wl * \delta_{\tau}*
\]
\[
  = ((\partial_t Tb) H * \delta_{\tau}*\fl* +  \tau(b(0)\delta + \partial_t bH)*\fl*\delta_{\tau}*
\]
\[
  +( b(0)\delta + \partial_t bH)*T\fl*\delta_{\tau} -
  Bh*\delta_{\tau}*\fl*
\]
SInce $\|\fl\|_{L^1(\bR)} =\lambda^{\frac{3}{2}} \|f_1\|_{L^1(\bR)}$ and
$\| T\fl\|_{L^1(\bR)} = \lambda^{\frac{5}{2}} \|f_1\|_{L^1(\bR)}$, every term in
the preceding expression is $O(\lambda^{\frac{3}{2}})$. Since $T$ is symmetric,
\begin{equation}
  \label{eqn:step9}
  \|[T,\Slb]\| = \|[T,(\Slb)^T]\| \le C\lambda^{\frac{3}{2}}.
\end{equation}
Note that by reasoning almost identical to that leading to the bound
\ref{eqn:step7.5},
\begin{equation}
  \label{eqn:step9.5}
  \|\dl-\dzl\| \le C\lambda.
\end{equation}
so
\begin{equation}
  \label{eqn:step10}
  \|T (\Slb)^T(\dl-\dzl)\| \le \|[ T, (\Slb)^T](\dl-\dzl)\| +
  \|(Slb)^TT (\dl-\dzl)\| \le C\lambda^{\frac{5}{2}}\|\dl\|
\end{equation}
